Approaching Optimal Duplicate Detection in a Sliding Window

### 2020-06-22 appendix.tex
COCOON preparing camera-ready

\section{Effects of the simulation's finiteness}
\label{app:finite}

>>>>

\section{SHF and queueing filter algorithms}\label{app:algo}
In this appendix, we give the pseudocode of our two structures, which we removed from the main part of the paper for page limit reasons.
\begin{algorithm}
	\caption{SHF \textsf{Setup}, \textsf{Lookup} and \textsf{Insert}}\label{alg:SHF}

	\begin{algorithmic}[1]
		\Function{Setup}{$M, w$}
		\Comment $M$ is the available memory, $w$ the size of the sliding window
		\State $h \gets$ hash function of codomain size $\lfloor \frac M{2w} - \frac 12 \log_2 w \rfloor$ bits
		\State $Q \gets \emptyset$ \Comment $Q$ is a queue of elements of size $h$
		\State $D \gets \emptyset$ \Comment $D$ is a dictionary $h \Rightarrow$  counter (of max value $w$)
		\EndFunction 
	\end{algorithmic}

	\begin{multicols}{2}
		\begin{algorithmic}[1]
			\Function{Insert}{$e$}
			\State $Q.\mathsf{Push\_Front}(h(e))$
			\State $D[h(e)]$++

			\If{$Q.\mathsf{length}() > w$}
			\State $h' \gets Q.\mathsf{Pop\_back}()$
			\State $D[h']$-{}-
			\If{$D[h'] = 0$}
			\State Erase key $D[h']$
			\EndIf
			\EndIf
			\EndFunction
		\end{algorithmic}

		\begin{algorithmic}[1]
			\item[]
			\Function{Lookup}{$e$}
			\If{$D[h(e)] > 0$}
			\State \Return \DUPLICATE
			\Else
			\State \Return \UNSEEN
			\EndIf
			\EndFunction
			\item[]
		\end{algorithmic}

	\end{multicols}
\end{algorithm}

\begin{algorithm}[]
	\caption{Queuing Filter \textsf{Setup}, \textsf{Lookup} and \textsf{Insert}}\label{alg:queuing}
	\begin{algorithmic}[1]
		\Function{Setup}{$\mathcal F, M, L, c$}
		\Comment $M$ is the available memory, $\mathcal F$ the subfilter structure, $L$ the number of subfilters and $c$ the number of insertions per subfilter
		\State subfilters $\gets \emptyset$
		\State counter $\gets 0$
		\State $m \gets \lfloor M/L \rfloor$
		\For{$i$ from $0$ to $L-1$}
		\State subfilters.push\_first$(\mathcal F.\mathsf{Setup}(m))$
		\EndFor
		\State \textbf{store} (subfilters, $L$, $m$, counter)
		%		\State\Return filter
		\EndFunction 
	\end{algorithmic}

	\begin{multicols}{2}
		\begin{algorithmic}[1]
			\Function{Lookup}{$e$}
			\For{$i$ from $0$ to $L-1$}
			\If{subfilters[i]$.\mathsf{Lookup(e)}$}
			\State \Return $\DUPLICATE$			
			\EndIf
			\EndFor
			\State \Return \UNSEEN
			\EndFunction
			\item[]
		\end{algorithmic}

		\begin{algorithmic}[1]
			\Function{Insert}{$e$}
			\State subfilters[0]$.\mathsf{Insert}(e)$
			\State counter$++$
			\If{counter == $c$}
			\State subfilters.pop()
			\State subfilters.push\_first($\mathcal F.\textsf{Setup}(m)$)
			\EndIf
			\EndFunction
		\end{algorithmic}
	\end{multicols}
\end{algorithm}
\section{Effects of the simulation's finiteness}
\label{app:finite}
